\textbf{NBA Party}

### 2017-04-07 init_model.rnw
After meeting with Eric at Arillaga.

<<echo=F,results='hide'>>=
require(data.table)
require(ggplot2)
load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/ndrink_estabs.RData')
drinks[, county := NULL]

@@

### We're careful to merge in ndrinking_estabs according to the PREV game played.
lines <- merge(lines, drinks, 
               by.x = c('last.game.loc', 'season'), 
               by.y = c('team',          'season'))
setkey(lines, date)
others <- grep("(party)|(last.game)", names(lines), value = T, invert = T)
setcolorder(lines, c(others, c('last.game.loc', 'party')))

require(sampling)
set.seed(04052017)
setkey(lines, season, last.game.loc)

@@

m = glm(outcome == 'W' ~ 0 + last.game.loc, data = var.creation, family = 'binomial')
coef <- m$coef
names(coef) <- gsub('last.game.loc', '', names(coef))
coef = data.table(last.game.loc = names(coef), coef)

@@

m = glm(outcome == 'W' ~ I(coef*(ndays.lgame==1)), data = training, family = 'binomial', subset = season < 2017) # Significant.

>>>>

<<echo=F,results='hide'>>=

### To Do: estimate coef by last.game.loc but exclude obs if last.game.loc == team
### i.e. just like in estimating party coef, we don't want to estimate effect of last 
### playing in boston if the team itself is boston.
### 
require(data.table)
require(ggplot2)
load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/ndrink_estabs.RData')
drinks[, county := NULL]

@@

inner.merge = merge(lines, drinks, 
                    by.x = c('last.game.loc', 'season'),
                    by.y = c('team',          'season'))
setkey(lines, season, team, date)
setkey(inner.merge, season, team, date)
outter = lines[!inner.merge]

### We're careful to merge in ndrinking_estabs according to the PREV game played.
## lines <- merge(lines, drinks, 
##                by.x = c('last.game.loc', 'season'), 
##                by.y = c('team',          'season'), all.x = T) ## Toronto raptors?
## setkey(lines, date)
## others <- grep("(party)|(last.game)", names(lines), value = T, invert = T)
## setcolorder(lines, c(others, c('last.game.loc', 'party')))

require(sampling)
set.seed(04052017)
setkey(lines, season, last.game.loc, date)

@@

m = glm(outcome == 'W' ~ 0 + last.game.loc, data = var.creation, family = 'binomial',
        subset = last.game.loc != team)
coef <- m$coef
names(coef) <- gsub('last.game.loc', '', names(coef))
coef = data.table(last.game.loc = names(coef), coef)

@@

m = glm(outcome == 'W' ~ 0 + coef + I(coef*(ndays.lgame==1)) + ndays.lgame + travel.dist,
        data = training, family = 'binomial', subset = season < 2017) # Significant.

synth  = cbind(coef, ndays.lgame = 1)
actual = lines[ndays.lgame == 1, list(meet.spread = mean(outcome == 'W')), keyby = last.game.loc]
preds  = predict(m, newdata = synth, type = 'response')
actual$preds = preds
require(ggplot2)
ggplot(actual, aes(x = meet.spread, y = preds, label = last.game.loc)) + 
    geom_point()+
    geom_label()
plot(actual$meet.spread, preds)
